--- 
title: "Life2 Code Compendium"
author: "Derek McCrae Norton"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

```{r color, echo = FALSE, results='asis'}
# crayon needs to be explicitly activated in Rmd
options(crayon.enabled = TRUE)
# Hooks needs to be set to deal with outputs
# thanks to fansi logic
old_hooks <- fansi::set_knit_hooks(knitr::knit_hooks, 
                                   which = c("output", "message", "error"))
```

# Introduction {#intro}

This document is intended to catalog and document all of the code for Life2 as well as how to use it.

## Locations

All code is currently versioned using SVN and can be found here:

Solution     | Location
------------ | --------
GBA          | http://06eyrad:81/svn/GBA
St Francis   | http://06eyrad:81/svn/st_francis
HL7          | http://06eyrad:81/svn/HL7
stac         | http://06eyrad:81/svn/stac


## General notes

- Currently Imidex does development in Eclipse using StatET. `.project` files are for that and not RStudio.
- 


## Bookdown Info

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
